---
title: "Reverse Engineering Project"
author: "Student names here"
date: "Date here"
output:
  html_document:
    theme: cerulean
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this notebook, we are reverse engineering the story, [As police struggle to solve homicides, Baltimore residents see an ‘open season for killing' (Washington Post)](https://www.washingtonpost.com/investigations/as-police-struggle-to-solve-homicides-baltimore-residents-see-an-open-season-for-killing/2018/12/26/7ee561e4-fb24-11e8-8c9a-860ce2a8148f_story.html)

## Load libraries

Loading required libraries for this analysis.

```{r echo=FALSE, message=FALSE}
library(tidyverse)
library(lubridate)
library(janitor)

```

## Load and Cleaning Data

In this section, describe the source of the data, write a basic data dictionary for data you are working with, and discuss any caveats or issues you discovered working with this data.

```{r}
# Load required data
# Load data
homicide_data <- read_csv("data/homicide-data.csv")

# Display it
homicide_data

# Path to data should be loaded from folder "data" i.e. read_csv("data/name_of_data.csv")

# Clean required data and prepare for analysis if needed. 

```

## Sentences to Engineer

In this notebook, we are reverse engineering five sentences from the story.

### Sentence 1

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: When coding to find the total number of murders in Baltimore 2014, there were 211. Then when you filter that to only the ones that are closed by arrest, it was 86. 86/211=0.407, which is about 41%

```{r}
# Put code to reverse engineer sentence here: City police made an arrest in 41 percent of homicides in 2014
# Display results of code below this codeblock
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "Baltimore")) |>
  filter(str_detect(disposition, "Closed by arrest"))
```

### Sentence 2

-   **Sentence text**: Community leaders and residents say that leaves hundreds of families who have been robbed of a loved one without a chance at seeing justice done. Of the 1,002 homicides between 2015 and the beginning of this year, just 252 — one out of every four — resulted in an arrest."
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
homicide_data |>
  filter(str_detect(reported_date, "2015") | str_detect(reported_date, "2016") | str_detect(reported_date, "2017"))|>
filter(str_detect(city, "Baltimore")) |>
filter(str_detect(disposition, "Closed by arrest"))


# Display results of code below this codebkloc

```

### Sentence 3

-   **Sentence text**: n Chicago, the homicide arrest rate has dropped 21 percentage points, in Boston it has dropped 12 points and in St. Louis it is down 9.
-   **Analysis summary**:
-   Chicago 2014 (125/418)
-   Chicago 2017 (56/654)
-   St Louis 2014 (65/160)
-   St Louis 2017 (64/202)
-   Boston 2014 (29/55)
-   Boston 2017 (22/54)

```{r}
#Chicago
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "Chicago")) 
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "Chicago")) |>
  filter(str_detect(disposition, "Closed by arrest"))
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "Chicago")) 
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "Chicago")) |>
  filter(str_detect(disposition, "Closed by arrest"))
#St Louis
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "St. Louis")) 
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "St. Louis")) |>
  filter(str_detect(disposition, "Closed by arrest"))
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "St. Louis")) 
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "St. Louis")) |>
  filter(str_detect(disposition, "Closed by arrest"))
#Boston
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "Boston")) 
homicide_data |>
  filter(str_detect(reported_date, "2014")) |>
  filter(str_detect(city, "Boston")) |>
  filter(str_detect(disposition, "Closed by arrest"))
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "Boston")) 
homicide_data |>
  filter(str_detect(reported_date, "2017")) |>
  filter(str_detect(city, "Boston")) |>
  filter(str_detect(disposition, "Closed by arrest"))

# Display results of code below this codeblock

```

### Sentence 4

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

### Sentence 5

-   **Sentence text**: [Paste in sentence to engineer here]
-   **Analysis summary**: [Write up two to three sentences describing the results of your analysis. Were you able to confirm the finding? If not, why not?]

```{r}
# Put code to reverse engineer sentence here

# Display results of code below this codeblock

```

-30-
